Modeling Two-Dimensional Vesicle Hydrodynamics with Hydrophobic Attraction Potential Simulations

### 2021-05-06 doc/main_jfm.tex
adding some texts

\begin{equation}
{\bf v}_\infty = v_{max}\left[ 1 - \left( \frac{y}{10R_0}\right)^2 \right]{\bf e}_x,
\end{equation}
%
where $v_{max}$ is the flow strength. $R_0$ is defined as the radius of the initial vesicle midplane.

\begin{figure}
\begin{center}
\includegraphics[width=0.3\textwidth]{N58_parabolic.eps}
\end{center}
  \caption{Vesicle under a parabolic flow where the strength of the flow $v_{max}=8.0$: 
The configuration is the state when $t=20000$.
  }
    \label{figure6}
\end{figure}

>>>>

\begin{equation}
{\bf v}_\infty = v_{max}\left[ 1 - \left( \frac{y}{wR_0}\right)^2 \right]{\bf e}_x,
\end{equation}
%
where $v_{max}$ is the flow strength and $w$ controls the shape of the flow. $R_0$ is defined as the radius of the initial vesicle midplane.

\begin{figure}
\begin{center}
\includegraphics[width=0.3\textwidth]{N58_parabolic.eps}
\end{center}
  \caption{Vesicle under a parabolic flow where the strength of the flow $v_{max}=8.0$ and the control parameter $w=10$. The configuration is the state when $t=20000$.
  }
    \label{figure6}
\end{figure}
